Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-08-07 tex/ms.tex
comment out craqzy calibration text in discussion

Fundamentally, calibration involves observing a `known' or `truth'
with an instrument, and using the observation to infer the effects of
the instrument.  However, we do not have knowledge of a single truth
for any object, only relative probabilities for what might be true.
In this sense, one should never use a single point estimate of the
calibration, the full distribution of the possible calibrations should
be inferred from our probabilistic knowledge of the calibration object
and forward propogated \citep[e.g.][]{lee11}. Once this is done, the only the
only distinction between 'calibration' objects and targets of interest
is the complexity of the model for the object and the level of
uncertainty in the calibration object spectrum.  If one is interested
in inferring parameters of interest of spectral models of
astrophysical objects, then there is no reason not to use those
objects themselves as calibration objects.

>>>>

% Fundamentally, calibration involves observing a `known' or `truth'
% with an instrument, and using the observation to infer the effects of
% the instrument.  However, we do not have knowledge of a single truth
% for any object, only relative probabilities for what might be true.
% In this sense, one should never use a single point estimate of the
% calibration, the full distribution of the possible calibrations should
% be inferred from our probabilistic knowledge of the calibration object
% and forward propogated \citep[e.g.][]{lee11}. Once this is done, the only the
% only distinction between 'calibration' objects and targets of interest
% is the complexity of the model for the object and the level of
% uncertainty in the calibration object spectrum.  If one is interested
% in inferring parameters of interest of spectral models of
% astrophysical objects, then there is no reason not to use those
% objects themselves as calibration objects.
